---
title: "Ozone Modelling pitching"
author: "Simon W Laufried"
date: "10/22/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## Background

#### As Ozone got depleted, through data we can find out the roor cause of the depleting ozone

## Modelling

#### the very first step is with modelling the ozone deplatation, but as many variables involve it is hard to determine which variable makes up the model  

We here display the modelling of each variables in effect to ozone

```{r modelling, echo=FALSE}
data <- na.omit(airquality)
data$date <- paste(data$Month, data$Day)
data$date <- as.Date(data$date, format = "%m %d")

model1 <- lm(Ozone ~ Solar.R, data = data)
model2 <- lm(Ozone ~ Wind, data = data)
model3 <- lm(Ozone ~ Temp, data = data)

plot(data$date, data$Ozone, xlab = "Dates", ylab = "Ozone", bty ="n", pch = 16)
model1lines <- predict(model1, newdata = data)
lines(data$date, model1lines, col = "red", lwd = 2)

model2lines <- predict(model2, newdata = data)
lines(data$date, model2lines, col = "blue", lwd = 2)

model3lines <- predict(model3, newdata = data)
lines(data$date, model3lines, col = "green", lwd = 2)
```


## Solution

#### it was really hard to see the effect of each variable, so we come up with a web that will plot each variable independently and shows only that you want to see with a click of a checkbox



